The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-30 Writeup/paper_v3.tex
add Semboloni baryonic effects reference

For the upcoming surveys to achieve their promise, their systematic error budgets must be below their statistical error budgets.
Systematic error budgets for weak lensing surveys typically include
astrophysical effects, such as intrinsic alignments of galaxy shapes
with large scale density fields \citep[e.g.,][]{2014arXiv1407.6990T} and the effect of baryons on the
matter power spectrum \citep[e.g.,][]{2011MNRAS.415.3649V}, as well as observational uncertainties such as
the ability to robustly infer shears from observed galaxy shapes or
photometric redshifts from their observed colors.
Given the expected sub-per cent statistical errors on upcoming surveys, systematic errors must be reduced from
 their typical level in the current state-of-the-art
 measurements that typically achieve $\sim 5$ per cent statistical
 errors at best
 \citep[e.g.,][]{2010A&A...516A..63S,2013MNRAS.432.2433H,2013ApJ...765...74J,2013MNRAS.432.1544M}.

>>>>

For the upcoming surveys to achieve their promise, their systematic error budgets must be below their statistical error budgets.
Systematic error budgets for weak lensing surveys typically include
astrophysical effects, such as intrinsic alignments of galaxy shapes
with large scale density fields \citep[e.g.,][]{2014arXiv1407.6990T} and the effect of baryons on the
matter power spectrum \rachel{\citep[e.g.,][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S}}, as well as observational uncertainties such as
the ability to robustly infer shears from observed galaxy shapes or
photometric redshifts from their observed colors.
Given the expected sub-per cent statistical errors on upcoming surveys, systematic errors must be reduced from
 their typical level in the current state-of-the-art
 measurements that typically achieve $\sim 5$ per cent statistical
 errors at best
 \citep[e.g.,][]{2010A&A...516A..63S,2013MNRAS.432.2433H,2013ApJ...765...74J,2013MNRAS.432.1544M}.
